### 2019-04-05 papers/journal/problem.tex
Added additional diagram to fix the problem statement confusion

\begin{forest}
 /tikz/every node/.append style={font=\sffamily,minimum size=1.0cm},
	for tree={
		edge+={->,thick},% uncomment for arrows
		draw,
		rounded corners,
		node options={align=center,},
		text width=1.7cm,
		calign=fixed edge angles, calign primary angle=-84,calign secondary angle=85,
	%	anchor=center,	
    %	calign=center,
	},
	where level=0{%
		parent anchor=children,
	}{%
		folder,
		grow'=0,
		if level=1{% this changes the edges from level 0 to nodes at level 1
			before typesetting nodes={child anchor=north},
			edge path'={(!u.parent anchor) -- ++(0,-5pt) -| (.child anchor)},
		}{},
	}
    [\textbf{VTS Search \\ Problems}, fill=white!20, parent, s sep=1mm,
	[\textbf{Existential Condition}, for tree={fill=fv, child}, 
	[BMC, for tree={fill=ai, child}]
	[SMT \\, for tree={fill=ai, child}]
	]
	[\textbf{Universal Condition}, for tree={fill=fv, child},
	[QBF, for tree={fill=ai, child}]
	]
	[\textbf{VTS Synthesis}, for tree={fill=fv,child}, 
	[Synthesis, for tree={fill=ai, child}]
	]
	]
\end{forest}
}
\end{adjustbox}
\vspace{0.01cm}

>>>>

\begin{forest}
 /tikz/every node/.append style={font=\sffamily,minimum size=1.0cm},
	for tree={
		edge+={->,thick},% uncomment for arrows
		draw,
		rounded corners,
		node options={align=center,},
		text width=1.7cm,
		calign=fixed edge angles, calign primary angle=-84,calign secondary angle=85,
	%	anchor=center,	
    %	calign=center,
	},
	where level=0{%
		parent anchor=children,
	}{%
		folder,
		grow'=0,
		if level=1{% this changes the edges from level 0 to nodes at level 1
			before typesetting nodes={child anchor=north},
			edge path'={(!u.parent anchor) -- ++(0,-5pt) -| (.child anchor)},
		}{},
	}
    [\textbf{VTS Search \\ Problems}, fill=white!20, parent, s sep=1mm,
	[\textbf{Existential Condition}, for tree={fill=fv, child}, 
	[BMC Sec.6.2, for tree={fill=ai, child}]
	[SMT Sec.6.1\\, for tree={fill=ai, child}]
	]
	[\textbf{Universal Condition}, for tree={fill=fv, child},
	[QBF \\ Sec.6.3, for tree={fill=ai, child}]
	]
	[\textbf{VTS Synthesis}, for tree={fill=fv,child}, 
	[Synthesis Sec.6.4, for tree={fill=ai, child}]
	]
	]
\end{forest}
}
\end{adjustbox}
\vspace{0.01cm}
